---
title: "p8105_hw5_yy2912"
author: "Roxana Yan"
date: "03/11/2019"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

#problem 1

```{r}
fill_iris = function(x){
    if (is.numeric(x)) {
      x = replace_na(x, mean(x[!is.na(x)], na.rm= TRUE))}
      else if (is.character(x)) {
      x= replace_na(x, "virginica")
      }
    }
 
iris_filled = map_df(iris_with_missing, fill_iris) 
```

#problem 2

```{r}
longstudy=list.files(path= "./data")

 dataframe = data_frame(files=longstudy)%>% 
  mutate(data=map(files, ~read.csv(str_c("./data/", .x))))%>%
  unnest()%>%
 pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observation"
 )%>%
 
   mutate(
    week=str_replace(week, "week_", ""),
    week=as.numeric(week),
    arm = substr(files, 1, 3),
    arm = recode(arm, "con" = "control",
                      "exp" = "experiment"),
    subject_id=substr(files,5,6),
    subject_id=as.numeric(subject_id))%>%

   select(-files)%>% 
select(arm,subject_id,week,observation)
```

#spaghetti plot

```{r}
dataframe %>% 
ggplot(aes(x = week, y = observation, group = subject_id, color = subject_id)) +
   geom_line() +facet_grid(. ~arm) + 
  labs(caption = "observations on each subject over time",
       x = "week",
    y = "observations")
```

#from the graph, the weekly observation did not vary much as time went by; however, in the experiment group, weekly observation increased as time increased.  

#problem 3

```{r}
sim_regression = function(n=30, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    xi1 = rnorm(n, mean = 0, sd = 1),
    yi = beta0 + beta1 * xi1 + rnorm(n, 0, 50)
  )
  
  ls_fit = lm(yi ~ xi1, data = sim_data)
  
    tibble(
    beta1_hat = broom::tidy(ls_fit)$estimate[2],
    p_value = broom::tidy(ls_fit)$p.value[2],
    alpha=0.05
  )
}
```

```{r}
output1 = 
  rerun(10000, sim_regression(30, 2, 0)) %>% 
  bind_rows
```

```{r}
beta1_list = list("beta1_1"  = 1, 
              "beta1_2"  = 2, 
              "beta1_3" = 3, 
              "beta1_4" = 4,
              "beta1_5" = 5,
              "beta1_6" = 6)
output = vector("list", length = 6)

for (i in 1:6) {
  output[[i]] = rerun(10000, sim_regression(beta1_list[[i]])) %>% 
    bind_rows}
```

```{r}
sim_results = 
  tibble(beta1 = c(1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = beta1, ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  
  select(-output_lists) %>% 
  unnest(estimate_dfs)
```

```{r}
sim_results%>%
  filter(p_value<0.05)%>%
  group_by(beta1)%>%
  summarize(power = sum(p_value < 0.05)/10000)%>% 
  ggplot(aes(x = beta1, y = power, color=beta1)) + 
  geom_line()+
  labs(caption = "association between effect size and power",
    x = "effect size",
    y = "power"
  ) 
```

From the plot, power increases as the effect size increases. 

```{r}
sim_results%>%
  group_by(beta1)%>%
  mutate(mean_beta1 = mean(beta1_hat))%>% 
  ggplot(aes(x = beta1, y = mean_beta1, color=beta1)) + 
  geom_line()+
  labs(caption = "association between true and measured beta1",
    x = "beta1",
    y = "average estimate of beta1"
  ) 
```

From the plot, the average estimate of beta1 increases as the true value of beta1 increases.

```{r}
sim_results%>%
  filter(p_value<0.05)%>%
  group_by(beta1)%>%
  mutate(mean_beta1_rej = mean(beta1_hat))%>% 
  ggplot(aes(x = beta1, y = mean_beta1_rej, color=beta1)) + 
  geom_line()+
  labs(caption = "association between true and measured beta1 when null is rejected",
    x = "beta1",
    y = "average estimate of beta1 only in samples for which the null was rejected"
  ) 
```

From the plot, only in samples for which the null was rejected, the average estimate of beta1 also increases as the true value of beta1 increases.

The sample average of beta1 across tests for which the null is rejected does not equal to the true value of beta1. The sample average is higher because when we only take the average of beta1s when the null is rejected, we excluded all zero beta1s (which only take the value of zero when the null is not rejected).
